---
output:
  html_document: default
  html_notebook: default
---
# Support Vector Machine

### Problem Statement:- Prepare support vector machines model for classifying the area under fire for foresfires data

### Data Understanding
```{r}
# Loading the Train Dataset
forest <- read.csv("~/desktop/Digi 360/Module 24/forestfires.csv")
head(forest)
```
```{r}
table(forest$size_category)
```

```{r}
#Deleting Month and day columns since they are already encoded.
forest <- forest[, -c(1,2)]
head(forest)
```

```{r}
# Loading required libraries
library(kernlab)
```

# Splitting Raw dataset

```{r}
library(caret)
train_index <- createDataPartition(forest$size_category, p=0.75, list=FALSE)

forest_train <- forest[train_index,]
forest_test <- forest[-train_index,]
```


```{r}
head(forest_train)
```


### Building the Model (Linear Kernel)

```{r}
forest_svm <- ksvm(size_category ~ . , data = forest_train, kernel = "vanilladot")
forest_svm
```

### Predicting on Test Data

```{r}
pred_svm <- predict(forest_svm, forest_test)
head(pred_svm)
```

The variable “pred_svm” stores the small and large levels corresponding to all the records. To read it properly let’s create a confusion matrix out of it.


### Confusion Matrix

```{r}
table(pred_svm, forest_test$size_category)
```

```{r}
agreement <- pred_svm == forest_test$size_category
table(agreement)
prop.table(table(agreement))
```

### Improving Model Performance. (RBF Kernel)

```{r}
forest_svm_rbf <- ksvm(size_category ~ . , data = forest_train, kernel = "rbfdot")
forest_svm_rbf
```

### Predictions on Test data

```{r}
pred_svm_rbf <- predict(forest_svm_rbf, forest_test)
head(pred_svm_rbf)
```

```{r}
agreement_rbf <- pred_svm_rbf == forest_test$size_category
table(agreement_rbf)
prop.table(table(agreement_rbf))
```

### Validation Observations

  - The accuracy with linear kernel is 98% 
  - The accuracy with rbf kernel is 85%. 

We can conclude that the given problem is linear in nature. 
