# Support Vector Machine

### Problem Statement:- To Predict Salary level of customers. 

```{r}
# Loading the Train Dataset
salary_train <- read.csv("~/desktop/Digi 360/Module 24/SalaryData_Train.csv")
head(salary_train)
```
```{r}
table(salary_train$Salary)
```
```{r}
salary_train$Salary <- ifelse(salary_train$Salary == ' <=50K', "Low", "High")
head(salary_train)
```

```{r}
table(salary_train$Salary)
```

The problem here is that the variable “Salary” in the char data type, which is a problem. As there are only two levels in this variable, high and low, hence we have to convert it into factor data type.

```{r}
salary_train$Salary <- as.factor(salary_train$Salary)
head(salary_train)
```

```{r}
# Loading required libraries
library(kernlab)
```

### Building the Model (Linear Kernel)


```{r}
salary_svm <- ksvm(Salary ~ . , data = salary_train, kernel = "vanilladot")
salary_svm
```


```{r}
# Loading the Test Dataset
salary_test <- read.csv("~/desktop/Digi 360/Module 22/Datasets-6/SalaryData_Test.csv")
head(salary_test)
```

```{r}
salary_test$Salary <- ifelse(salary_test$Salary == ' <=50K', "Low", "High")
head(salary_test)
```

```{r}
table(salary_test$Salary)
```
```{r}
salary_test$Salary <- as.factor(salary_test$Salary)
head(salary_test)
```

### Predicting on Test Data

```{r}
pred_svm <- predict(salary_svm, salary_test)
head(pred_svm)
```

The variable “pred_nb” stores the high and low levels corresponding to all the records. To read it properly let’s create a confusion matrix out of it.


### Confusion Matrix

```{r}
table(pred_svm, salary_test$Salary)
```

```{r}
agreement <- pred_svm == salary_test$Salary
table(agreement)
prop.table(table(agreement))
```

### Improving Model Performance. (RBF Kernel)

```{r}
salary_svm_rbf <- ksvm(Salary ~ . , data = salary_train, kernel = "rbfdot")
salary_svm_rbf
```

### Predictions on Test data

```{r}
pred_svm_rbf <- predict(salary_svm_rbf, salary_test)
head(pred_svm_rbf)
```

```{r}
agreement_rbf <- pred_svm_rbf == salary_test$Salary
table(agreement_rbf)
prop.table(table(agreement_rbf))
```

### Validation Observations

  - The accuracy with linear kernel is 85% 
  - The accuracy with rbf kernel is 85%. 

We can conclude that the given problem is linear in nature. 
